Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-11 draft.tex
yet more bibliography; some minor edits

As social choice moves to the web, the

the need for relaxing the assumptions

@@

We then show how minimax regret can be used to drive the elicitation

@@

\paragraph{Query types}

\paragraph{Strategies}

@@

% we discuss the different forms of queries and develop several query strategies 
\paragraph{Query types}

>>>>

%As social choice moves to the web, the
%the need for relaxing the assumptions of classical social choice

@@

We then show how minimax regret can be used to drive the elicitation in order to ask informative queries in order to

@@

\paragraph{Query types}
We distinguish between queries asked to the voters and questions asked to the chair.

Another common type or queries are {\em top-k}, asking to each voter his $k$ most alternatives.

In particular, we want to acquire constraints of the type:
\[ w_{i} - w_{+1i} \geq \lambda (w_{i+1} - w_{i+2}) \]

\paragraph{Elicitation strategies}

@@

% we discuss the different forms of queries and develop several query strategies
